Differential invariant signatures for planar Lie group transformations of images

### 2021-09-14 paper/newpaper.tex
Added reference to Olver

\section{Introduction}
The appearance of a fixed object in a set of images can vary markedly depending upon such variables as pose and position relative to the camera, even though the object itself does not change. This is even more marked in scenes that consist of multiple objects at different distances and orientations to the camera against a fixed background. The appearance of each individual object will then chnge in different ways as a constant camera motion or other such transformation is applied. Typically the individual transformations will appear as the action of an element of a planar Lie group, for example the affine, or projective groups, or an angle-preserving transformation from the conformal group, depending upon the camera model.

@@

The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Invariants for this group have been computed using points~\citep{Gros1992,Suk2000}, geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and differential and joint invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19}.

@@

\subsection{The Projective Group}

>>>>

\section{Introduction}
The appearance of a fixed object in a set of images can vary markedly
depending upon such variables as pose and position relative to the camera,
even though the object itself does not change. This is even more marked in
scenes that consist of multiple objects at different distances and
orientations to the camera against a fixed background. The appearance of
each individual object will then change in different ways as a constant
camera motion or other such transformation is applied. Typically the
individual transformations will appear as the action of an element of a
planar Lie group, for example the affine, or projective groups, or an
angle-preserving transformation from the conformal group, depending upon
the camera model.

@@

The group that has been of particular interest for image analysis is the
projective group, because of its ubiquity in camera models. Invariants for
this group have been computed using points~\citep{Gros1992,Suk2000},
geometric moments~\citep{Suk2004}, curvature~\citep{Hann2002a}, and
differential and joint
invariants~\citep{Hubert2007,Arora2009,Kogan2014,Li19, Olver2020}. In
particular Olver, in \citet{Olver2020}, uses the same approach as we do in
\S\ref{sec:projective}, but with a different moving frame normalization to
produce a different set of projective image invariants.

@@

\subsection{The Projective Group}\label{sec:projective}
